### 2016-01-18 papers/CAFe/HIPS-paper/performance.tex
Near final pass.

It is important to note that the emphasis of this work is to explore and explain the new
syntax and execution semantics of a CAFe application.  A thorough examination of potential
performance gains (if any) using CAFe for parallelization of code is beyond the scope of
this paper.  The primary purpose of CAFe is to combine the parallel features of Fortran coarrays
--- executing a \emph{single} program --- with concurrent execution of separate tasks executing on
potentially heterogeneous hardware.  However, the relative performance of computation on
a cluster of GPUs compared with the necessary communication of halo information is
of interest; especially considering complete exchance of halo data between multiple
coarray images \emph{and} between each individual host image and its subimage (an attached
OpenCL device).

@@

This section shows and compares performance measurements for: 1. Memory bandwidth usage on
GPU; 2. Computaional time on GPU; 3. Halo Communication time (total plus breakdown to and
from device and MPI); 4. Total time scaling on ACISS; 5. Comparison with OpenACC
(hopefully).

\subsection{Halo Transfer Performance}

The current implementation does \emph{not} take advantage of optimization strategies such
as prefetching of array tiles (including halos) into OpenCL local memory or of loop
unrolling on the OpenCL device.

>>>>

It is important to note that the emphasis of this work is to explore and explain the new
syntax and execution semantics of a CAFe application.  A thorough examination of potential
performance gains (if any) using CAFe for parallelization of code is beyond the scope of
this paper.  The primary purpose of CAFe is to combine the parallel features of Fortran coarrays
--- executing a \emph{single} program --- with concurrent execution of separate tasks executing on
potentially heterogeneous hardware.  However, the relative performance of computation on
a cluster of GPUs compared with the necessary communication of halo information is
of interest, especially considering that a complete exchance of halo data involves communication
between multiple
coarray images \emph{and} between each individual host image and its subimage (an attached
OpenCL device).

@@

This section shows and compares performance measurements for: 1. Computational time on the GPU
of the interior domain;
2. Computational time on the CPU of the shared boundary regions; and 3. Halo communication time.

%%\subsection{Halo Transfer Performance}

The current implementation does \emph{not} take advantage of optimization strategies such
as prefetching of array tiles (including halos) into OpenCL local memory.
